---
title: "linear model from Web"
author: "Alex Moreno"
date: "Summer 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
lmr = lm(SIMS~ARM,data=data)
abline(lmr)
```

Positive linear plot. Some points scattered but mostly at a positive rate.

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
The numerical results conclude with a value of 0.686

### Inferential  (Build model.1)

```{r}
summary(lmr)
newdata=c(GRIP=94, ARM=88)
```

The minimum value is -3.6467. The Q1 value is -0.7502. The median is -0.0285. The max is 3.0770.

#### Predict at target point

```{r}
predictSIMS=predict.lm(lmr, newdata=data.frame(GRIP=94, ARM=88))
print(predictSIMS)
```

The target point for SIM~ARMS is 0.7063

#### scatterplot with model fit
  
```{r}
plot(lmr)
```

Positive line in the Q-Q means this is normal and accurate.

## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
grp = lm(SIMS~GRIP,data=data)
abline(grp)
```

Positive linear relation in this plot graph.

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

The numerical value is 0.63984

### Inferential  (Build model.2)

```{r}
summary(grp)
newdata=c(GRIP=94, ARM=88)
```

The minimum value is -2.9295. The Q1 value is -0.8708. The Q3 value is .8039. The median is -0.1219. The max is 3.3494.


#### predict model.2 at target point

```{r}
predictGRIP=predict.lm(grp, newdata=data.frame(GRIP=94, ARM=88))
print(predictGRIP)
```

The target point prediction value is -0.5361


#### now add the model fit to our plot for model.2
  
```{r}
plot(grp)
```

Plots look accurate as they are following the data given.

## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
data2=lm(SIMS~ARM+GRIP, data=data)
summary(data2)
```


The minimum value is -3.1846. The median is -0.0641. The max is 2.8634.

### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point

```{r}
predict.lm(data2, newdata=data.frame(GRIP=94, ARM=88))
```

  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3

```{r}
anova(lmr, data2)
```

145 residual degrees of freedom for SIMS~ARM is 145, while SIMS~ARM+GRIP is 144. Difference of 1. Model 2 has a sum of squares of 29.45. Model 2 has a p-value of 0.000004994.

### Model.2 vs Model.3

```{r}
anova(grp, data2)
```

Residual freedom of values for SIMS~GRIP is 145 and SIMS~ARM+GRIP is 144. Same difference of 1 as before. Model 2 has a sum of squares of 54.64. Model 2 has a p-value of 0.000000001495.


## Informally compare Model.1 with model.2

```{r}
anova(lmr, grp)
```

The residual degrees of freedom for model 1 and 2 are at 145 for both. No difference here. No p-value given for these comparisons.

